---
title: "mca task"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r education, echo=TRUE}
#Insert packages and education data
install.packages("FactoMineR")
library(FactoMineR)
Education = read.table(file.choose(), header=T, sep=",")
head(Education)
names(Education)

#Change variables to factor format
Education$SCHOOL<- as.factor(Education$SCHOOL)
Education$LIT<- as.factor(Education$LIT)
Education$EDATTAIN<- as.factor(Education$EDATTAIN)
Education$YRSCHOOL<- as.factor(Education$YRSCHOOL)
summary(Education)

#Change values indicating not in universe, missing, or unknown to NA
Education[,7:9][Education[,7:9]==9]<- NA
Education[,7:9][Education[,7:9]==0]<- NA
Education[, 10][Education[, 10]==90]<- NA
Education[, 10][Education[, 10]==98]<- NA

#Omit NAs
Education.noNA = na.omit(Education)
x=Education.noNA[,7:10]
```


Multiple Correspondence Analysis
```{r plot, echo=TRUE, fig.height=12, fig.width=12}
x.mca=MCA(x) #multiple correspondence analysis
plot(x.mca)
summary(x.mca) #90 percent is goal for dimension

```

Summary of Plots
MCA factor Map
  Q1- Those who completed 12-13 years of school completed a secondary degree or university. 
  Q2&3- Those who completed less than primary education or never attended school were in school          for few years and are often illiterate.
  Q4- People who completed primary were in school between 7 and 11 years usually. 
  
  
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
